%% google scholar GB/T 7714

\begin{thebibliography}{2}
	\setlength{\baselineskip}{25pt}
	
	\bibitem{SAGIWSN2014}
	M. Maamar, J. Liu and W. Liu, \emph{A new lightweight link quality based reputation model for Space-Air-Ground Integrated Wireless Sensor Network (SAGIWSN)}, Electronics, Computer and Applications, 2014 IEEE Workshop on. IEEE, 2014: 230-236.
	
	\bibitem{GIG}
	P. Wolfowitz, \emph{Global Information Grid (GIG) Overarching Policy}, US Department of Defense, directive, 2002 (8100.1).
	
	\bibitem{shenrongjun}
	R. Shen, \emph{Some Thoughts of (Chinaese) Integrated Space-Ground Network System}, Engineering Science, 2006, 10: 003 (in Chinese).
	
	\bibitem{SAG2013}
	H. Liu, J. Zhang and L. L. Cheng, \emph{Application examples of the network fixed point theory for space-air-ground integrated communication network}, Ultra Modern Telecommunications and Control Systems and Workshops (ICUMT), 2010 International Congress on. IEEE, 2010: 989-993.
	
	\bibitem{SCR}
	K. L. Heninger, \emph{Specifying software requirements for complex systems: New techniques and their application}, Software Engineering, IEEE Transactions on, 1980 (1): 2-13.
	
	\bibitem{nasa1}
	S. Easterbrook, J. Callahan, \emph{Formal methods for verification and validation of partial specifications: A case study}, Journal of Systems and Software, 1998, 40(3): 199-210.
	
	\bibitem{hangdian}
	S. Meyers, S. White, \emph{Software requirements methodology and tool study for A6-E technology transfer}, Grumman Aerospace Corp. , Report, 1983.
	
	\bibitem{timedCSP}
	G. M. Reed, A. W. Roscoe, \emph{A timed model for communicating sequential processes}, Automata, Languages and Programming, Springer Berlin Heidelberg, 1986: 314-323.
	
	\bibitem{CRSM}
	A. C. Shaw, \emph{Communicating real-time state machines}, Software Engineering, IEEE Transactions on, 1992, 18(9): 805-816.
	
	\bibitem{TA}
	R. Alur, D. L. Dill, \emph{A theory of timed automata}, Theoretical computer science, 1994, 126(2): 183-235.
	
	\bibitem{processcontrol}
	N. G. Leveson, M. P. E. Heimdahl, H. Hildreth, et al. \emph{Requirements specification for process-control systems}, Software Engineering, IEEE Transactions on, 1994, 20(9): 684-707.
	
	\bibitem{ChenSTeC}
	Y. Chen \emph{Stec: A location-triggered specification language for real-time systems}, Object/Component/Service-Oriented Real-Time Distributed Computing Workshops (ISORCW), 2012 15th IEEE International Symposium on. IEEE, 2012: 1-6.
	
	\bibitem{WuSTeC}
	H. Wu, Y. Chen and M. Zhang, \emph{On Denotational Semantics of Spatial-Temporal Consistency Language--STeC}, Theoretical Aspects of Software Engineering (TASE), 2013 International Symposium on. IEEE, 2013: 113-120.
	
	\bibitem{ChenSTeC2014}
	Y. Chen, Y. Zhang, \emph{A hybrid clock system related to STeC language}, Software Security and Reliability-Companion (SERE-C), 2014 IEEE Eighth International Conference on. IEEE, 2014: 199-203.
	
	\bibitem{ZhangSTeC}
	Y. Zhang, F. Mallet and Y. Chen, \emph{Timed Automata Semantics of Spatial-Temporal Consistency Language STeC}, Theoretical Aspects of Software Engineering Conference (TASE), 2014. IEEE, 2014: 201-208.
	
	\bibitem{observationmission1}
	N. Bianchessi, J. F. Cordeau, J. Desrosiers, et al., \emph{A heuristic for the multi-satellite, multi-orbit and multi-user management of earth observation satellites}, European Journal of Operational Research, 2007, 177(2): 750-762.
	
	\bibitem{maude}
	T. Luan, Y. Chen, J. Wang, \emph{Maude Rewriting System of Specification Language STeC for Real-time System}, Computer Engineering, 2013, 39(10): 57-62 (in Chinese).
	
	\bibitem{Uppaal}
	G. Behrmann, A. David, K. G. Larsen, \emph{A tutorial on uppaal}, Formal methods for the design of real-time systems. Springer Berlin Heidelberg, 2004: 200-236.
	
	
\end{thebibliography}
